\chapter{Results}\label{ch:results}

\section{Cyclic parts}\label{sec:cyclic-part-results}

\begin{lemma}
	\label{lem:cyclic-part-no-short-cut}
	Let $P$ be a cyclic $k$-part. Let $S$ be an edge cut separating $P$ into two components $P_1$ and $P_2$ such that $P_1$ contains a cycle. Then it holds that ${|S| \geq |S(P)\cap S(P_2)|}$.
\end{lemma}

\begin{proof}
	Note that $S(P)\cap S(P_i)$ contains all of the semiedges from $P$, which are in $P_i$ after cutting the edges, for both $i\in\{1,2\}$.
	
	Let $G$ be a cubic graph with cyclic edge-connectivity $k$ and let $S_G$ be a cycle-separating $k$-edge-cut such that one of the cyclic $k$-parts of $G-S_G$ is $P$. Let us denote the other cyclic $k$-part by $Q$. Suppose that there is such edge cut $S$, for which it holds that $|S| < |S(P)\cap S(P_2)|$. 
	
	When severing an edge $e$, let the new created semiedges be denoted as $e_1$ and $e_2$. For $i\in\{1,2\}$ denote by $E_i$ the set of edges such that $$E_i=\{e ~|~ e\in S_G, \exists i \in \{1,2\}: e_i\in S(P_i)\}$$
	
	so edges from $S_G$, for which after their severing, one of the new created semiedges is in $P_i$. We prove that $S_G=E_1\cup E_2$. Since $E_i\subseteq S_G$ for both $i\in\{1,2\}$, it is evident that $E_1\cup E_2\subseteq S_G$. For each edge in $S_G$, one of the resulting semiedges is in $P$ and the other in $Q$. Suppose otherwise, so there is an edge $e$, for which both resulting semiedges are in one of $P$ or $Q$. Without loss of generality, let both be in $P$. Then $S_G-\{e\}$ is a cycle-separating edge-cut in G with $k-1$ edges, contradicting the fact that $G$ is cyclically $k$-edge-connected. Since from each edge $f\in S_G$ one of the resulting semiedges is in $P$, say $f_1$, it must be in $P_1$ or $P_2$, thus $S_G\subseteq E_1\cup E_2$.
	
	Note that $S\cup E_1$ is an edge-cut in $G$, separating it into components $P_1$ and a partial junction of $P_2$ and $Q$. By assumption $P_1$ contains a cycle and $Q$ is a cyclic part, thus also contains a cycle, which means that $S\cup E_1$ is cycle-separating.
	
	We prove that $|S(P)\cap S(P_2)|=E_2$. Since $E_2$ contains all edges from $S_G$, which create a semiedge in $S(P)\cap S(P_2)$, it holds that $|E_2|\leq |S(P)\cap S(P_2)|$. For the other inequality, we see that all semiedges in $S(P)\cap S(P_2)$ were created by the cut $S_G$, specifically by its subset $E_2$. Each edge from $E_2$ creates only one such semiedge. Suppose the contrary, so there would be some edge $e\in E_2$, for which both semiedges $e_1$ and $e_2$ would be in $P_2$. It is evident that $S_G-\{e\}$ is a cycle-separating edge-cut in $G$ with $k-1$ edges, contradicting the fact that $G$ is cyclically $k$-edge-connected. Because of this $|S(P)\cap S(P_2)|\leq |E_2|$. 
	
	 Note, that $|S| < |E_2|$, since $|S| < |S(P)\cap S(P_2)|$ and $|S(P)\cap S(P_2)|=|E_2|$. It holds that $S\cap E_1=\emptyset$, since $S$ is an edge cut in $P$ and there are no edges left in $P$ from $E_1$, as each of them was severed when creating $P$. Also $E_1\cap E_2=\emptyset$. Suppose the contrary, so there would be some edge $e$ which is in $E_1$ and $E_2$. This would mean that both of its incident vertices would be in $P$, which contradicts the assumption that $G$ is cyclically $k$-edge-connected, as we have proved above. However, this would mean that $|S\cup E_1|< |E_1\cup E_2| = |S_G|=k$, thus $S\cup E_1$ is a cycle-separating cut with at most $k-1$ edges, contradicting the assumption that $G$ is cyclically $k$-edge-connected.
	
	\todo{uviesť ilustrácie}
\end{proof}

\todo{Poriadnejšie definovať cyklickú k-časť, nech nie je viazaná na pôvodný graf}
\todo{toto nižšie hovorí podobné len to je asi trocha jednoduchšie napísané...}
\begin{lemma}
	Let $M$ be a cyclic $k$-part. Then there is no edge cut $S$ of size $l$ separating $M$ into two multipoles $M_1$ and $M_2$ such that $M_1$ contains a cycle and $k_1$ semiedges from the former $k$-pole $M$, for which $l+k_1 < k$.
\end{lemma}

\begin{proof}
	Let $G$ be a cubic graph with $\zeta(G)=k$ such that $G=M*N$ for some cyclic $k$-part $N$. We know that at least one of these graphs exists, since $M$ is a cyclic $k$-part. Suppose that there would be such edge cut $S$ of size $l$ in $M$ separating it into two multipoles $M_1$ and $M_2$ such that $M_1$ contains a cycle and $k_1$ semiedges from $M$ and $l+k_1 < k$. Let us denote the set of $k_1$ semiedges from $M$ as $K_1$ and the set of links in $G$ created by the junction of semiedges from $K_1$ as $E_1$. We can see that $S\cup E_1$ is a cycle-separating edge cut in $G$ and $|S\cup E_1|=l+k_1 < k$, contradicting the fact that $\zeta(G)=k$.
\end{proof}

\begin{lemma}[{{\cite[Lemma 5.1]{Rajnik_phd}}}]\label{lem:rajnik5.1}
	Let $M$ be an $s$-pole with girth at least $k$ different from a $k$-cycle for some $s\leq k$. Then $|M| \geq 2k - 4$.
\end{lemma}

\begin{theorem}
	Let $M_1$ be a cyclic $k$-pole such that for each edge-cut $S$ of size $l$ separating $M_1$ into $M_1^1$ and $M_1^2$ such that $M_1^1$ contains a cycle and $k_1$ semiedges from $M_1$, it holds that $l+k_1\geq k$. Let $M_2$ be a cyclic $k$-part, and let both $M_1$ and $M_2$ be different from the cycle of length $k$ or $k\leq 5$. Let $G$ be the junction of $M_1$ and $M_2$. Then $\zeta(G)=k$ unless the girth of $G$ is smaller than $k$.
\end{theorem}

\begin{proof}
	Let us denote the $k$-cut obtained after the junction $M_1*M_2$ by $S$. Suppose by contradiction that $G$ has girth at least $k$ and contains a cycle separating edge cut $T$ of minimal size, such that $|T|=l<k$ and it separates $G$ into two components $X_1$ and $X_2$. Note that in this case $\zeta(G)=l$. Let $A_1,A_2,A_3,A_4$ denote the subgraphs of $G$ induced by $V(X_1)\cap V(M_1), V(X_1)\cap V(M_2), V(X_2)\cap V(M_2), V(X_2)\cap V(M_1)$ respectively. Let $a,b,c,d,e$ and $f$ denote the number of edges connecting $A_1$ and $A_2$, $A_1$ and $A_3$, $A_1$ and $A_4$, $A_2$ and $A_4$, $A_3$ and $A_4$, $A_2$ and $A_3$ respectively \todo{ilustrácia}.
	
	Next let $r_i=|\delta(A_i)|$ for each $i\in\{1,2,3,4\}$. We can see that each of such $r_i$ is determined by the values of $a,b,c,d,e$ and $f$, for instance $r_1=a+b+c$. We say that each of $A_1, A_2,A_3$ and $A_4$ is non-empty, let us prove it by contradiction. Suppose that some $A_i$ for $i\in\{1,2,3,4\}$ is empty. We shall look at both cases that can happen:
	
	\begin{itemize}
		\item Case 1: $A_1$ or $A_4$ is empty. Then $M_2$ would contain the whole cyclic $l$-pole $X_1$ or $X_2$ which leads to a contradiction by \cref{lem:cyclic-part-no-short-cut}.
		\item Case 2: $A_2$ or $A_3$ is empty. Then $M_1$ would contain the whole cyclic $l$-pole $X_1$ or $X_2$. Suppose $A_2$ is empty, so $M_1$ contains $X_1$, the proof for empty $A_3$ is analogous. Let us denote the number of semiedges of $M_1$ contained in $X_1$ as well as $k_1$. Since $X_1$ is an $l$-pole, there is an edge cut $S_1$ of size $l-k_1$ separating $X_1$ from the rest of $M_1$. We know that $X_1$ contains a cycle and $(l-k_1)+k_1=l<k$, contradicting the assumption about $M_1$.
	\end{itemize}

	Since all cases lead to a contradiction, each of $A_i, i\in\{1,2,3,4\}$ is non-empty.
	
	From the sizes of $S$ and $T$ we know that
	
	\begin{align}
		a+b+d+e &= k, \label{abde_eq_k}\\
		l=c+b+d+f &< k. \label{cbdf_smaller_k}
	\end{align}

	We now show that for each $i\in\{1,2,3,4\}$ at least one of the inequalities $r_i\geq k$ or $r_{i+1}\geq k$ is true, taking the indices modulo 4. Suppose to the contrary that there exists such $i\in\{1,2,3,4\}$ for which $r_j\leq k-1$ for both $j\in\{i, i+1\}$. Let us look at the properties of one of such $A_j$. We know that it contains less than $k$ semiedges, say $m$.
	
	\begin{enumerate}
		\item If $A_j$ is in $M_1$, it must be acyclic. Suppose that it would contain a cycle. Similarly as before, let us denote the number of semiedges of $M_1$ contained in $A_j$ as well as $k_1$. Since $A_j$ is an $m$-pole, there is an edge cut $S_1$ of size $m-k_1$ separating $A_j$ from the rest of $M_1$. Since $A_j$ contains a cycle and $(m-k_1)+k1=m<k$ this contradicts the assumption about $M_1$.
		\item If $A_j$ is in $M_2$, it must be acyclic because of $\cref{em:cyclic-part-no-short-cut}$ and the fact that is has less than $k$ semiedges.
	\end{enumerate}

	We see, that both $A_i$ and $A_{i+1}$ are acyclic. Thus, we have that $|A_j|\leq r_j-2\leq k-3$ for both $j\in \{i, i+1\}$. By denoting $M$ as $G[A_i\cup A_{i+1}]$ we have $|M|\leq 2k-6$ ($A_i$ and $A_{i+1}$ are vertex disjoint). Note that $M$ is by its definition one of the multipoles $X_1, X_2, M_1,$ or $M_2$. This means that $M$ is cyclic and $|M|\geq k$ due to the girth of $G$ which must be at least $k$. From $k\leq |M|\leq 2k+6$ we have $k\geq 6$ so by the assumption of the theorem $M_1$ and $M_2$ are different from the $k$-cycle. Also both of $X_1$ and $X_2$ are different from $k$-cycles since they have less than $k$ semiedges. Therefore $M$ is not a $k$-cycle and it is a cyclic multipole with at most $k$ semiedges and girth at least $k$, so by \cref{lem:rajnik5.1}, $|M| \geq 2k - 4$, contradicting the fact that $|M|\leq 2k-6$.
	
	Thus for each $i\in\{1,2,3,4\}$ we have $r_i\geq k$ or $r_{i+1}\geq k$, from which it follows that
	
	\begin{align}
		r_1 =a+b+c\geq a+b+d+e=k \text{ and } r_3 =b+e+f \geq a+b+d+e=k\label{r1r3}
	\end{align}

	or
	
	\begin{align}
		r_2 =a+d+f \geq a+b+d+e=k \text{ and } r4 =c+d+e\geq a+b+d+e=k\label{r2r4}
	\end{align}

	is true. After summing, Inequalities \cref{r1r3} imply that $c+f\geq a+2d+e\geq a+e$ and Inequalities \cref{r2r4} imply that $c+f\geq a+2b+e\geq a+e$. In both cases we have obtained $c+f\geq a+e$. However by Inequality \cref{cbdf_smaller_k} we have 
	$$l=b+c+d+f<a+b+d+e=k$$
	
	so $c+f<a+e$, which leads to a contradiction.
\end{proof}

SK: Ak by toto bola pravda, tak ak by sme vedeli nájsť pre každé $k$ takú cyklickú $k$-časť (vieme to modifikovať aj na cyklický $k$-pól pre ktorý platí predpoklad) ktorý po spojení nevytvorí krátky cyklus, tak ak dostaneme na vstupe cyklický $k$-pól (pre $k>5$ iný ako $k$-cyklus), stačí nám overiť či platí predpoklad, a ak hej, tak to je cyklická k-časť. Bude to pravdepodobne jednoduchšie ako zisťovať cyklickú súvislosť po napojení universal $k$-adjunct.

\section{Cyclic part inflations}\label{sec:cyclic-part-inflations}

\begin{definition}[{{\cite[Definition 10]{HISTs}}}]
	Let $G$ be a graph and let $H$ be a cubic graph. Then $H$ is called an inflation of $G$ if $H$ contains a 2-factor $F$ consisting of chordless cycles such that the graph obtained from $H$ by contracting each cycle of $F$ to a vertex is isomorphic to $G$. By $I(G)$ we denote the set of all inflations of $G$.
\end{definition}

Informally speaking, one can obtain an inflation of $G$ by expanding each of its vertices to a cycle with the length same as the degree of the respective vertex in $G$. We can extend this definition, by allowing expanding each vertex of the original graph into a cyclic $k$-part, where $k$ is the degree of the respective vertex.

\todo{Definovať kedy vrcholy korešpondujú cyklickej časti v grafe, teda keď pospájam cyklické časti $P_1,\cdots, P_n$ do výsledku $G$, tak kedy nejaká množina vrcholov $V$ korešponduje v $G$ s $P_i$. Resp. treba to definovať?}

Let $G$ be a graph and $V$ a subset of its vertices. By \textit{contracting} $V$ in $G$ we obtain a new graph $G'$, such that:
\begin{itemize}
	\item For the vertices of $G'$ it holds that $V(G') = (V(G)-V)\cup \{v\}$ where $v$ is a new vertex.
	\item Let $E$ be a set containing such edges from $G$, which are incident with one vertex in $V$ and one in $V(G)-V$. Formally, ${E=\{xy~|~xy\in E(G), x\in V, y\notin V\}}$. Let $E'$ be a set of edges, which are incident with two vertices from $V$, formally ${E'=\{xy ~|~ xy\in E(G), x\in V, y\in V\}}$. Finally let $E''$ be a set of new edges, such that $E''=\{vy~|~ xy\in E, x\in V\}$.
	
	 For the edges of $G'$ it holds that ${E(G')=(E(G)-E')\cup E''}$.
\end{itemize}

\begin{definition}
	\label{def:cyclic-part-inflation}
	Let $G$ be a graph and let $H$ be a cubic graph resulting from performing partial junctions on cyclic parts $P=\{P_1,\cdots,P_n\}$. Let $V=\{V_1,\cdots, V_n\}$ be a partition of $V(H)$ such that for each $i$ from 1 to $n$ the set $V_i$ corresponds to the cyclic part $P_i$. Then $H$ is called a \textit{cyclic part inflation} of $G$ if the graph obtained from $H$ by contracting each set $V_i\in V$ into a single vertex is isomorphic to $G$. The set of all cyclic part inflations of $G$ is denoted by $I_P(G)$.
\end{definition}

For inflations it has been proved, that in specific cases if the original graph is $k$-connected, then each of its inflations is cyclically $k$-connected.

\begin{theorem}[{{\cite[Theorem 11]{HISTs}}}]
	Let $k \geq 3$ and let $G$ be a $k$-connected graph with girth at least $k$. Then every $H \in I(G)$ is cyclically $k$-edge-connected.
\end{theorem}

We can prove a similar theorem for cyclic part inflations. The proof is similar to the one used to prove the mentioned theorem for inflations, however it is needed to tackle some more edge-cases.

\begin{theorem}
	Let $k\geq 3$ and let $G$ be a $k$-connected graph with girth at least $k$. Then every  $H\in I_P(G)$ is cyclically $k$-edge-connected.
\end{theorem}

\begin{proof}
	Let $H\in I_P(G)$. For each vertex $v\in V(G)$, denote the unique cyclic part in $H$ corresponding to it (as in \cref{def:cyclic-part-inflation}) by $P_v$. We say that a cycle $C$ in $H$ is \textit{traversal} if there are two distinct vertices $v_1,v_2$ in $G$ with $V(P_v)\cap V(C)\neq \emptyset$ for both $v\in\{v_1,v_2\}$, so it goes through two unique cyclic parts in $H$. Otherwise we say that $C$ is \textit{non-traversal}, meaning $C\subseteq P_v$ for some $v\in V(G)$.
	
	Suppose by contradiction, that $H$ is not cyclically $k$-edge-connected. Then $H$ has an edge cut $S$ with $|S|\leq k-1$ such that $H-S$ has precisely two components $D_1$ and $D_2$ and both contain a cycle.
	
	Let $D_i^G$ be the subgraph of $G$ induced by the vertex set $$\{x\in V(G)~|~ V(P_x)\cap V(D_i)\neq \emptyset\}$$
	so vertices from $G$, whose corresponding cyclic parts in $H$ have at least one vertex overlapping with the component $D_i$. Let us define sets $S_V^G$ and $S_E^G$ as
	\begin{align*}
		S_V^G &= \{x\in V(G) ~|~ E(P_x)\cap S\neq \emptyset\} \\
		S_E^G &= \{e\in S ~|~ \forall x\in V(G): e\notin E(P_x) \}.
	\end{align*}

	This means, that $S_V^G$ are vertices from $G$ whose corresponding cyclic parts contain at least one edge from $S$ and $S_E^G$ are edges from $S$ which are not a part of any cyclic part, or in other words connect two vertices in $G$ and connect two cyclic parts in $H$. It can be seen that ${V(D_1^G)\cap V(D_2^G)=S_V^G}$, since the set contains vertices, whose corresponding cyclic parts contain edge from $S$, thus are split into the two components.
	
	It is evident that $S_V^G\cap S_E^G=\emptyset$, since one set contains vertices and the other one edges, meaning $|S_V^G\cup S_E^G|=|S_V^G|+|S_E^G|$. We prove that $|S_V^G\cup S_E^G|\leq |S|$. For each element $x\in S_V^G\cup S_E^G$ there is at least one representant in $S$, not overlapping with the representants of other elements. There are two possibilities for $x$:
	\begin{enumerate}
		\item The element $x$ is a vertex, thus $x\in S_V^G$. The representants in $S$ are in this case the links in $P_x$ which are in the edge-cut $S$. No other element from $S_V^G\cap S_E^G$ has overlapping representants, if it is some $y\in S_V^G$ different from $x$ it is evident that the links from $P_y$ will be different. On the other hand, if it is some $e\in S_E^G$, these elements have different representants, as it is explained next.
		\item The element $x$ is an edge, thus $x\in S_E^G$. Note that these are the edges from $S$, which are not a part of any cyclic part. For the sake of readability, len us denote it as $e$. The representant of $e$ in $S$ will be that edge itself. Same as before, no other element $y\neq e$ from $S_V^G\cap S_E^G$ has overlapping elements. If $y$ is from $S_V^G$, its representants are inner links from $P_y$, thus not containing $e$. If $y$ is from $S_E^G$, its representant is an edge different from $e$.
	\end{enumerate} 
	
	This means, that $|S_V^G\cup S_E^G|\leq |S|$, which means after putting everything together that $$|S_V^G|+|S_E^G|=|S_V^G\cup S_E^G|\leq |S|\leq k-1.$$

	Suppose that $V(D_i^G)-S_V^G\neq\emptyset$ for each $i\in \{1,2\}$, meaning there is a whole cyclic part in both $D_1$ and $D_2$. Then $G-S_v^G-S_E^G$ has two components $F_1^G$ and $F_2^G$. The number of vertex disjoint paths from a vertex of $F_1^G$ to a vertex of $F_2^G$ in $G$ is at most $|S_V^G|+|S_E^G|\leq k-1$, which contradicts by Menger's Theorem that $G$ is $k$-connected.
	
	Therefore we may assume without loss of generality that $V(D_1^G)-S_V^G=\emptyset$, meaning there is no whole cyclic part in $D_1$.
	
	Another thing to note is that in this case the component $D_2$ must contain at least one unsplit cyclic part, or in other words $V(D_2^G)-S_V^G\neq\emptyset$. Suppose that $V(D_2^G)-S_V^G=\emptyset$, which would mean that each cyclic part has been split by $S$. However $G$ is $k$-connected, thus $|V(G)|>k$ and since $S$ contains an edge from each of the cyclic parts it must hold that $|S|\geq |V(G)|>k$ which contradicts that $|S|\leq k-1$.
	
	By assumption $D_1$ contains a cycle, say $C_1$. Suppose that this cycle is non-traversal, thus $C_1\subseteq P_v$ for some $v\in V(G)$. It must hold that $v\in S_V^G$, since there is no unsplit cyclic part in $D_1$, meaning $P_v$ has been split by $S$. Let $V_1,$ and $V_2$ be the vertices from $P_v$ incident with a dangling edge in $D_1$ and $D_2$ respectively. Let $E_1$ and $E_2$ be the respective dangling edges. Let us denote the set $E_L(P_v)\cup S$ as $S_P$. This set contains the links from $P_v$ which were split by the cut $S$. By \cref{lem:cyclic-part-no-short-cut} it holds that $|S_P|\geq|E_2|$. Let us denote the set of links in $H$ from which result dangling edges in $E_2$ after severing edges from $S$ as $L_2$. We can now create an edge cut $S'=(S-S_P)\cup L_2$, which is cycle separating in $H$ and it holds that $|S'|\leq |S|\leq k-1$. Since both components now contain a whole cyclic part, this contradicts the assumption that $G$ is $k$-connected, as it was proved before.
	
	This means, that the cycle in $D_1$, say $C_1$ must be traversal. Thus $C_1$ corresponds to a closed trail in $D_1^G$, say $C_1^G$. Since the girth of $G$ is at least $k$ and every closed trail contains a cycle, we have $|V(C_1^G)|\geq k$, which contradicts that $V(C_1^G)\subseteq V(D_1^G)\subseteq S_V^G$ and $|S_V^G|\leq k-1$.
	
\end{proof}
